---
title: "Assignment 2 (A0111277M A0124106X A0124177H A0129519X A0130771M)"
author: "Ning Yu, Wong Jun Hao Marcus, Peter Haw Han Beng, Han Zixuan, Daniel Wong Sing Dong"
date: "2/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1.
#### Suppose we have a matrix of 1s and 0s. We want to create a vector as follows: for each row of the matrix, the corresponding element of the vector will be either 1 or 0, depending on whether the majority of the first c elements in the row is 1 or 0. Here c will be a parameter which we want to control. Create a function to perform this task.

```{r}
rowsWithMajorityOnes <- function(m, c) {
  v = (length=dim(m)[1])
  for (i in 1:dim(m)[1]) {
    v[i] <- ifelse(sum(m[i,1:c])>(c/2), 1, 0)
 }
  return(v)
}
```

The following is an example to test the rowsWithMajorityOnes function.
```{r}
m <- matrix(nrow=5, ncol=7) 
m <- apply(m, c(1,2), function(x) sample(c(0,1),1))
c = 5

m
rowsWithMajorityOnes(m, c)
```

## Question 2.
#### Create a script to crawl all property data from SRX.com.sg.

```{r}

```