---
title: "Assignment 3 - Team 6 (A0111277M A0124106X A0124177H A0129519X A0130771M)"
author: "Ning Yu, Wong Jun Hao Marcus, Peter Haw Han Beng, Han Zixuan, Daniel Wong Sing Dong"
date: "2/19/2018"
output: html_document
---

## Question 1.
#### Run your codes in Assignment 2 to crawl at least 100 pages of SRX data. Clean it up and explore it using the techniques learned in class. Write a 2-page report in Word about your findings.

After crawling the first 100 pages of search results on the SRX website, the following code was applied to clean the data.
  
```{r}
require(magrittr)
require(dplyr)
require(mice)

srxData <- read.csv("srx (Team 6).csv", stringsAsFactors = TRUE)
srxData$X <- NULL # Gets rid of row indices
na_count <-sapply(srxData, function(y) sum(is.na(y)))
na_count

# Asking: (1) Assigned "NA" to observations with no asking price, and (2) added a new column that indicates which observations have an asking price and which do not.
suppressWarnings(srxData$Asking <- ifelse(srxData$Asking=="View to offer", NA, as.numeric(gsub(",", "", gsub("\\$", "", srxData$Asking)))))
srxData$AskingAvail <- !is.na(srxData$Asking)

# PSF: Added two new columns to differentiate PSF price (land basis) and PSF price (built-up basis).
srxData$PSFLand <- as.numeric(gsub(".*[(]Built-up[)].*", "", gsub(",", "", gsub(".*\\$([0-9,]+(?=\\s+psf\\s+[(]Land[)])).*", "\\1", srxData$PSF, perl = TRUE))))
srxData$PSFBuilt <- as.numeric(gsub(".*[(]Land[)].*", "", gsub(",", "", gsub(".*\\$([0-9,]+(?=\\s+psf\\s+[(]Built-up[)])).*", "\\1", srxData$PSF, perl = TRUE))))

# Model: Closed unclosed round brackets in the data.
srxData$Model <- factor(gsub("(?!.*[)])([(].*+)", "\\1)", srxData$Model, perl = TRUE))

# District & HDB.Town: Manually assign a HDB.Town to the sole observation with an NA in both "District" and "HDB Town"
srxData[which((is.na(srxData$HDB.Town) == TRUE) & (is.na(srxData$District) == TRUE)),]$HDB.Town <- "Queenstown"

# Developer
  srxData$Developer <- factor(toupper(gsub("(?i)limited(?-i)", "LTD", srxData$Developer)))
  srxData$Developer <- factor(gsub("[(]*(?i)PRIVATE[)]*(?-i)", "PTE", srxData$Developer, perl = TRUE))
  srxData$Developer <- factor(gsub("(BUKI SEMABWANG ESTATES LTD)|(BUKIT SEMABWANG ESTATES LTD)", "BUKIT SEMBAWANG ESTATES LIMITED", srxData$Developer))
  srxData$Developer <- factor(gsub("CITY DEVELOPMENT LTD", "CITY DEVELOPMENTS LTD", srxData$Developer))
  srxData$Developer <- factor(gsub("ORGANISATION", "ORGANIZATION", srxData$Developer))
  srxData$Developer <- factor(gsub("FAIRVIEW DEVELOPMENT PTE LTD", "FAIRVIEW DEVELOPMENTS PTE LTD", srxData$Developer))
  srxData$Developer <- ifelse(grepl("HDB",srxData$Property.Type),
                                      "HOUSING DEVELOPMENT BOARD",srxData$Developer)

# Floor
srxData$Floor <- addNA(srxData$Floor)
levels(srxData$Floor) <- ifelse(grepl("01",levels(srxData$Floor)),"GROUND",levels(srxData$Floor))

# Area: (1) Introduced a conversion factor for converting sqm to sqft, and (2) added two new columns to differentiate area (land basis) and area (built-up basis).
sqmToSqftConvFactor <- 10.7639
srxData$AreaLand <- ifelse(grepl("sqft",srxData$Area)|
                             is.na(srxData$Area),
                           as.numeric(gsub(".*(([(]Built-up[)])|(sqm)).*", "", gsub(",", "", gsub("^.*(\\s|^)([0-9,]+(?=\\s+sqft\\s+[(]Land[)])).*", "\\2", srxData$Area, perl = TRUE)))), 
                           as.numeric(gsub(".*(([(]Built-up[)])|(sqft)).*", "", gsub(",", "", gsub("^.*(\\s|^)([0-9,]+(?=\\s+sqm\\s+[(]Land[)])).*", "\\2", srxData$Area, perl = TRUE))))*sqmToSqftConvFactor)
srxData$AreaBuilt <- ifelse(grepl("sqft",srxData$Area)|
                              is.na(srxData$Area),
                            as.numeric(gsub(".*(([(]Land[)])|(sqm)).*", "", gsub(",", "", gsub("^.*(\\s|^)([0-9,]+(?=\\s+sqft\\s+[(]Built-up[)])).*", "\\2", srxData$Area, perl = TRUE)))), 
                            as.numeric(gsub(".*(([(]Land[)])|(sqft)).*", "", gsub(",", "", gsub("^.*(\\s|^)([0-9,]+(?=\\s+sqm\\s+[(]Built-up[)])).*", "\\2", srxData$Area, perl = TRUE))))*sqmToSqftConvFactor)

# Tenure
levels(srxData$Tenure) <- ifelse(grepl("Freehold",levels(srxData$Tenure)),"FREEHOLD",levels(srxData$Tenure))
levels(srxData$Tenure) <- ifelse(grepl("946 years from 01/01/1938",levels(srxData$Tenure)) | grepl("946 years from 23/06/1938",levels(srxData$Tenure)) | grepl("947 years from 05/10/1934",levels(srxData$Tenure)),"999 years",levels(srxData$Tenure))

# Furnish
srxData$Furnish <- addNA(srxData$Furnish)
```

With the data cleaned, the following visualisations were done.

```{r}
require(ggplot2)
require(ggthemes)
```

#### PSF of Private Properties by Region
```{r}
# to create a df classifies means PSF by District
psf.pp.df = as.data.frame(tapply(srxData$PSFBuilt, srxData$District, mean, na.rm=TRUE))
colnames(psf.pp.df) = c("PSF")
psf.pp.df$District = rownames(psf.pp.df)
rownames(psf.pp.df) = 1: dim(psf.pp.df)[1]
# sort the factor level of $District in ascending order of the corresponding PSF value (for plotting)
psf.pp.df <- psf.pp.df[order(psf.pp.df$PSF), ]
psf.pp.df$District <- factor(psf.pp.df$District, levels = psf.pp.df$District[order(psf.pp.df$PSF)])
# plot the bar chart 
ggplot(psf.pp.df) + geom_bar(aes(x=District, y= PSF),stat="identity", fill="lightpink") + coord_flip()  + labs(x="", y="PSF") + ggtitle("Average PSF of Private Properties by Region") + theme(axis.text.y=element_text(size = rel(0.8))) + theme_minimal() 
```

#### PSF of HDB by Region
```{r}
# to create a df classifies means PSF by HDB.Town
psf.hdb.df = as.data.frame(tapply(srxData$PSFBuilt, srxData$HDB.Town, mean, na.rm=TRUE))
colnames(psf.hdb.df) = c("PSF")
psf.hdb.df$HDB.Town = rownames(psf.hdb.df)
rownames(psf.hdb.df) = 1: dim(psf.hdb.df)[1]
# sort the factor level of $Distrct in asending order of the corrsponding PSF value (for ploting)
psf.hdb.df <- psf.hdb.df[order(psf.hdb.df$PSF), ]
psf.hdb.df$HDB.Town <- factor(psf.hdb.df$HDB.Town, levels = psf.hdb.df$HDB.Town[order(psf.hdb.df$PSF)])
# plot the bar chart 
ggplot(psf.hdb.df) + geom_bar(aes(x=HDB.Town, y= PSF),stat="identity", fill="lightblue") + coord_flip()  + labs(x="", y="PSF") + ggtitle("Average PSF of HDB by Region") + theme(axis.text.y=element_text(size = rel(0.8))) + theme_minimal() 
```

#### Variation in Asking Price for Different Property Types
```{r}
ggplot(srxData,aes(x=Property.Type,y=Asking)) + geom_boxplot() + ylim(0,3000000) + coord_flip() + labs(title="Variation in Asking Price for Different Property Types", y="Asking Price")
```

#### Variation in Asking Price with Number of Bathrooms
```{r}
ggplot(srxData, aes(x=Bathrooms,y=Asking)) + ylim(0,10000000) + geom_point(position=position_jitter(w=.2,h=.05)) + xlim(1,8) + labs(title="Variation in Asking Price with Number of Bathrooms", y="Asking Price")
```
